Figures

### 2020-04-02 manuscript/appendix.Rmd
formatting fixes

---
title: "Appendix"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage{colortbl}
---

\def\figurename{Figure A}
\def\tablename{Table A}

@@

>>>>

---
title: "Appendix S1"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage{colortbl}
- \usepackage{setspace, caption}
- \usepackage{times}
- \DeclareCaptionFont{blah}{\doublespacing\normalsize\fontseries{n}\fontfamily{ptm}\selectfont}
- \captionsetup{font=blah}
- \pagenumbering{gobble}
---

\def\figurename{Figure S\hspace{-0.3em}}
\def\tablename{Table S\hspace{-0.3em}}

@@

\centering
# Appendix S1

\begin{flushleft}
Title: Granular measures of agricultural land-use influence lake nitrogen and phosphorus differently at macroscales.

Authors: Joseph Stachelek, W. Weng, C.C. Carey, A.R. Kemanian, K.M. Cobourn, T. Wagner, K.C. Weathers, P.A. Soranno

Journal: Ecological Applications
\end{flushleft}

\vspace{6em}

### 2020-04-02 manuscript/figures.Rmd
formatting fixes

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{colortbl}
- \usepackage{caption}
- \usepackage{float}
---

@@

>>>>

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{colortbl}
- \usepackage{setspace, caption}
- \usepackage{float}
- \usepackage{times}
- \DeclareCaptionFont{blah}{\doublespacing\normalsize\fontseries{n}\fontfamily{ptm}\selectfont}
- \captionsetup{font=blah}
- \setcounter{page}{37}
---

@@

\renewcommand{\listfigurename}{Figure legends}
\doublespacing
\renewcommand*\numberline[1]{Figure\,#1:\space}
\makeatletter
\renewcommand*\l@figure[2]{\noindent#1\par}
\makeatother
\listoffigures
